Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-09 lqg-strings.tex
Added connection EoM section to main file
Added new field EoM section

>>>>

\subsection{The Connection Equation} \label{sec:omega-eom}

Varying our action w.r.t connection $\omega ^{m n} _{c}$ gives the vanishing of world-sheet torsion $\mathcal{T}^{i} _{a b}$ as
\begin{equation} \label{eqn:variation-wrt-omega}
	\frac{\delta S_{P A}}{\delta \omega ^{m n} _{c}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:vanishing-torsion}
	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} G_{\mu \nu} = 0 .
\end{equation}

\subsection{The New Field Equation} \label{sec:v-eom}

The equation of motion for the new field $v^{l}$ gives a constraint on said field and the embbeding fields $X^{\mu} _{i}$
\begin{equation} \label{eqn:variation-wrt-v}
	\frac{\delta S_{P A}}{\delta v^{l}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:v-and-X-constraint}
	g^{a b} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} G_{\mu \nu} = 0 .
\end{equation}
